Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex

\noindent Data Citations, Code Availability, Data Availability

\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scientific Data analysis paper
\end{itemize}

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
in one participant.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired participants.

@@

\subsection*{Code availability}

\todo[inline]{provide supporting source code; explain how/where other may
access data underlying the analysis}

\todo[inline]{if using custom code for dataset generation/processing: indicate
how code can be accessed (including restrictions to access)}

\todo[inline]{include infos on versions of used software}

\todo[inline]{any specific variables or parameters used to generate, test, or process the current dataset?}

>>>>

\noindent Data Citations, Code Availability
\begin{itemize}
    \item draft for Data Citation is done
    \item draft for Code and Data Availability is done (other analysis paper do
        it pretty amateurish); will look at the ``how to write an excellent
        data availability statement'' at springernature.com
\end{itemize}

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
in one participant.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired participants.

@@

\subsection*{Data and code availability}

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI and annotation data, analysis scripts to generate the results as well
as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
accessible as Datalad (RRID:SCR_003931) datasets.
